{\boldmath Pseudoscalar top-Higgs coupling: Exploration of $\mathrm{CP}$-odd observables to resolve the sign ambiguity }

### 2016-02-23 Paper_ttbarH_Draft.tex
a few changes made by KK to Sec. II

diagrams are displayed in Fig.~\ref{fig1}, with the first two
rows containing the $q\bar{q}$ and $gg$ $s$-channel diagrams, and
the last one depicting the $gg$ $t$-channel diagrams. By exchanging the gluon

@@

d\sigma =\sum_{\substack{b{\ell}^+\nu_l \\ \tiny{\mathrm{spins}}}}\,\sum_{\substack{\bbar {\ell}^-\nubar \\ \mathrm{\tiny{spins}}}}\left(\frac{2}{\Gamma_t}\right)^2\,d\sigma(gg\to t(n_t)\tbar (n_{\tbar})H)\,d\Gamma(t(n_t)\to b{\ell}^+\nu_{\ell})\,d\Gamma(\tbar (n_{\tbar})\to \bbar {\ell}^-\nubar),

@@

boson, and $d\Gamma(t(n_t)\to b{\ell}^+\nu_{\ell})$ and
$d\Gamma(\tbar (n_{\tbar})\to \bbar {\ell}^-\nubar)$ are the
differential decay widths of a top with spin vector $n_t$ and an
anti-top with spin vector $n_{\tbar}$, respectively. Also, the vectors

@@

\cite{kawasaki} and in particular for $t\tbar$ production both in

@@

\cite{ale1,*ale2,*ale3,*ale4}. \par We will outline now how to derive

>>>>

diagrams are displayed in Fig.~\ref{fig1}, where the first two
rows show the $q\bar{q}$ and $gg$ $s$-channel diagrams, and
the last one depicts the $gg$ $t$-channel diagrams. By exchanging the gluon

@@

d\sigma =\sum_{\substack{b{\ell}^+\nu_l \\ \tiny{\mathrm{spins}}}}\,
   \sum_{\substack{\bbar {\ell}^-\nubar \\ \mathrm{\tiny{spins}}}}\left(\frac{2}{\Gamma_t}\right)^2\,
   d\sigma(gg\to t(n_t)\tbar (n_{\tbar})H)\,
   d\Gamma(t\to b{\ell}^+\nu_{\ell})\,
   d\Gamma(\tbar \to \bbar {\ell}^-\nubar),

@@

boson, and $d\Gamma(t\to b{\ell}^+\nu_{\ell})$ and
$d\Gamma(\tbar \to \bbar {\ell}^-\nubar)$ are the
differential decay widths for an unpolarized top and
anti-top, respectively. Also, the vectors

@@

\cite{kawasaki} and for $t\tbar$ production both in

@@

\cite{ale1,*ale2,*ale3,*ale4}. \par

We will outline now how to derive
